---
title: "Baseball Player Analysis 2"
author: "AnuAchankunju"
date: "Friday, November 06, 2015"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(dplyr)
library(GGally)
library(scales)
library(memisc)
library(reshape)
library(gridExtra)
```


#Baseball players Performance Exploration By Anu Achankunju
#========================================================

## About
This data set contains the  performance and physical aspects information of 1157 Baseball players like like height, weight and handedness of 1157 players. 


```{r echo=FALSE, warning=FALSE}
### Load and inspect data
setwd('C:\\Users\\320002667\\Box Sync\\NanoDegree\\M5_Make Effective Visualization\\NanoDegree_DA_P5\\data')
player_df<-read.csv('baseball_data.csv')
```

### Structure of the  dataset
Let's run some basic functions to examine the structure and schema of the data set.

```{r echo=TRUE, warning=FALSE}
dim(player_df)
names(player_df)
summary(player_df)
summary(player_df$Handedness)

```


Some initial observations are:

* There are 1577 observations of 7  variables.
* **Name** appears to be the unique identifier.
* **Home Runs** is a discrete variable. 
* All other variables except Handedness seem to be continuous numeric values.


##Exploratory Plots

###Relationship of Handedness with batting average and Home Runs


```{r echo=FALSE, warning=FALSE}
#ggplot(player_df , aes(x=factor(Height.cm.), y=Home.Runs)) + stat_summary(fun.y="mean", geom="bar")
ggplot(player_df , aes(x=factor(Handedness), y=HomeRuns)) + stat_summary(fun.y="mean", geom="bar")
ggplot(player_df , aes(x=factor(Handedness), y=BattingAverage)) + stat_summary(fun.y="mean", geom="bar")

```

###Rletionship of Height with batting average and Home Runs

```{r echo=FALSE, warning=FALSE}
 ggplot(aes(x=Height, y=HomeRuns), data = player_df)+
  geom_point()+
  xlab('Height')+
  ylab('Home Runs')+
  ggtitle('Home Runs Vs Height')+
  geom_smooth(color = 'red', linetype=1)

 ggplot(aes(x=Height, y=BattingAverage), data = player_df)+
  geom_point()+
  xlab('Height')+
  ylab('BattingAverage')+
  ggtitle('BattingAverage Vs Height')+
  geom_smooth(color = 'red', linetype=1)

ggplot(player_df , aes(x=factor(Height), y=HomeRuns)) + stat_summary(fun.y="mean", geom="bar")

#ggplot(player_df , aes(x=factor(Height), y=BattingAverage, color=Handedness)) + stat_summary(fun.y="mean", geom="bar")


```


###Rletionship of Weight with batting average and Home Runs

```{r echo=FALSE, warning=FALSE}
 ggplot(aes(x=Weight, y=HomeRuns), data = player_df)+
  geom_point()+
  xlab('Weight')+
  ylab('Home Runs')+
  ggtitle('Home Runs Vs Weight')+
  geom_smooth(color = 'red', linetype=1)

 ggplot(aes(x=Weight, y=BattingAverage), data = player_df)+
  geom_point()+
  xlab('Weight')+
  ylab('BattingAverage')+
  ggtitle('BattingAverage Vs Weight')+
  geom_smooth(color = 'red', linetype=1)
```


